%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{}
\name{Abdullah}{Basulaib}
%\position{{\enskip\cdotp\enskip}}
%\address{}

\mobile{(+1) 416-887-4294}
\email{basulaiba@gmail.com}
% \homepage{}
\github{basulaib}
\linkedin{basulaiba}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Postmedia Network Inc.}
  {}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Junior Software Developer}
% How the letter is opened
\letteropening{\textbf{Dear Hiring Manager,}}
% How the letter is closed
\letterclosing{\textbf{Sincerely,}}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}
  {}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
\textbf{I'm a York University Computer Science graduate. I'm a passionate, motivated and hard-working developer. I have lead many of  the projects throughout my university years, with clear and effective communication while working in a safe, respectful and open environment. I express my thoughts and ideas loud and clear to the team, and accept and appreciate reply and feedback as well. Additionally, I am also willing to learn new knowledge and experiences.
}
\lettersection{About Me}
\textbf{During my contribution to the Soccer Twitter project, I took leadership of the project and managed the project's specifications and deadlines, along with having the responsibility of laying the foundation of the project. I designed and wrote the base foundation of the project, using real-time data coming from Twitter. I was instrumental in developing the data flow and organization of the incoming data. \\
\\
I am also attentive to continuously look out for difficulties or bugs. When we faced a bug with the real-time data stream from Twitter, I suggested and implemented that we do the data cleaning after the data collection and not during. This led to 50\% faster data processing and analysis.\\
\\
When I am not working on projects, I like to spend my time learning more about frameworks, libraries, and programming languages. That includes reading documentation, exploring, and experimenting. I am always ready and happy to try any new technology. I took the time to learn Flask to make my own web projects. 

}
\lettersection{Why Me?}
\textbf{I believe I fit for the Junior Software Developer position as I bring my curiosity, drive, and effective communication skills for this position. I love working with teams and learning a lot with them, it is an experience I'm looking forward to. Thank you for considering my application and I look forward to hearing from you regarding this position.
}
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
